Network Configuration Synthesis with Abstract Topologies

### 2016-11-14 paper/abstraction/paper.tex
remove git message

A final concept is the $\Mincut(1)$ constraint between the spine role S and N[1--2]. It says that any spine router has at least one path to any node in the neighbor N1 (and N2) role. Such annotations are useful for a "one big switch" abstraction \cite{Casado:2010} in which a complex, unstructured network is represented as a single node. As another use case, an ISP backbone can be modeled by dividing the network into separate geographic regions with two roles per region---one for the border routers and another for the network core. Mincut annotations can describe the degree of fault tolerance both within regional cores and across regions.

@@

%Configuration synthesis for network configurations is challenging for a number of reasons. First, although \sysname polices specify network-wide routing behavior, actual configurations are per-device and run distributed algorithms to compute routes. Thus the compiler must ensure that the result of the distributed interaction of devices correctly implements the policy including when failures occur. Second, \sysname must find configurations that work for any valid concrete network topology matching the user-specified abstraction. Finally, \sysname must ensure that the resulting configurations can be evolved incrementally so that local changes to the topology ensure that only local changes to configurations are required to ensure global routing correctness.

%In this section, we formalize the \sysname language and describe how \sysname translates policies to a graph-based intermediate representation.

%\subsection{Methane Language}

\begin{figure}[t]\small
  \begin{minipage}[t]{\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     pol     &::=& p_1, \dots, p_n & \textit{policy} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT a & \textit{path preferences}  \\
     t       &::=& \$x \BNFALT d.d.d.d/[d..d] \hspace{1.5em} & \textit{predicate} \\
     a      &::=& agg(t, r_1 \rightarrow r_2) & \textit{aggregation} \\
     r       &::=& l \BNFALT \emptyset \BNFALT \In \BNFALT \Out \BNFALT r_1 \cup r_2 \BNFALT & \textit{regular path} \\
             &   & r_1 \cap r_2 \BNFALT r_1 \cdot r_2 \BNFALT \NOT r \BNFALT r^* \\
%         &\BNFALT& \emptyset & \textit{empty set} \\
%         &\BNFALT& \In & \textit{internal loc} \\
%         &\BNFALT& \Out & \textit{external loc} \\
%         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
%         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
%         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
%         &\BNFALT& \NOT r & \textit{path negation} \\
%         &\BNFALT& r^* & \textit{iteration} \\
  \end{array} \]%

@@

The first step for the \sysname compiler is to build the product graph (PG), a data structure that is amenable to joint analysis of the topology and routing policy. As a precursor to this step, we convert the routing policy syntax in \S\ref{sec:overview} to a core language based on regular expressions, shown in Figure~\ref{fig:syntax}.
%
A policy has one or more constraints, each an aggregation or a path constraint. Path constraints have a test on a destination prefix and a list of regular expressions describing network paths. Regular paths are defined over network locations, where each location is either a router inside the operator's network, or an external neighbor connected to that network. Values \In\ and \Out\ will match any internal and external location respectively. There are two types of predicates, as shown. A test for a concrete prefix $d.d.d.d/[d..d]$ matches a range of IP prefixes (\EG, 10.0.1.0/[24..32]) where metavariable $d$ represents an integer.

>>>>

A final concept is the $\Mincut(1)$ constraint between the spine role S and N[1--2]. It says that any spine router has at least one path to any node in the neighbor N1 (and N2) role. Such annotations are useful for a ``one big switch" abstraction \cite{Casado:2010} in which a complex, unstructured network is represented as a single node. As another use case, an ISP backbone can be modeled by dividing the network into separate geographic regions with two roles per region---one for the border routers and another for the network core. Mincut annotations can describe the degree of fault tolerance both within regional cores and across regions.

@@

\begin{figure}[t]\small
  \begin{minipage}[t]{\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     pol     &::=& p_1, \dots, p_n & \textit{policy} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT a & \textit{path preferences}  \\
     t       &::=& \$x \BNFALT d.d.d.d/[d..d] \hspace{1.5em} & \textit{predicate} \\
     a      &::=& agg(t, r_1 \rightarrow r_2) & \textit{aggregation} \\
     r       &::=& l \BNFALT \emptyset \BNFALT \In \BNFALT \Out \BNFALT r_1 \cup r_2 \BNFALT & \textit{regular path} \\
             &   & r_1 \cap r_2 \BNFALT r_1 \cdot r_2 \BNFALT \NOT r \BNFALT r^* \\
  \end{array} \]%

@@

The first step for the \sysname compiler is to build the product graph (PG), a data structure that is amenable to joint analysis of the topology and routing policy. As a precursor to this step, we convert the routing policy syntax in \S\ref{sec:overview} to a core language based on regular expressions, shown in Figure~\ref{fig:syntax}.
%
A policy has one or more constraints, each an aggregation or a path constraint. Path constraints have a test on a destination prefix and a list of regular expressions describing network paths. Regular paths are defined over network locations, where each location is either a router inside the operator's network, or an external neighbor connected to that network. Values \In\ and \Out\ will match any internal and external location respectively. There are two types of predicates, as shown. A test for a concrete prefix $d.d.d.d/[d..d]$ matches a range of IP prefixes (\EG, 10.0.1.0/[24..32]) where metavariable $d$ represents an integer. A prefix template test {\small\$x}, for variable $x$, represents a collection of many tests, one for each prefix represented by the template.
